### 2015-07-02 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added content to hose stream report, primarily in the procedure section

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
\caption[East Structure floor layout]{East Structure floor layout. All dimensions are in meters.}
\label{fig:east_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
\label{fig:west_general_plan}
\end{figure}

@@

\section{Instrumentation}
\label{sec:Instrumentation}
Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}. There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/BDPs}
\caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
\label{fig:BDPs}
\end{figure}

@@

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor equipped with a combination nozzle. A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}). After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This process was repeated an additional time.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 29 and 30}
\label{fig:test_29_30_pic}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 29 and 30 in multiple ways. First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_setup}. Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened, and each stream was applied for 30 seconds again.

Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied at the "far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the "near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle. A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:test_29-32_setup}) in the fixed position. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds. Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed. This entire procedure was repeated an additional time.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
\caption[East Structure layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 31 and 32 in multiple ways. First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:test_33_34_setup}. Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern. Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. These steps were repeated for narrow fog and wide fog streams. Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
\caption[East Structure layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier

Tests 18 and 19 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a handline with a combination nozzle located at the south side, double doors on the first level of the West Structure. The difference between the two tests was that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Tests 18 and 19 repeated an identical process three times, one time for each hose stream pattern. To begin the process, the nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

>>>>

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
\caption[East Structure Layout]{East Structure floor layout. All dimensions are in meters.}
\label{fig:east_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
\label{fig:west_general_plan}
\end{figure}

@@

\subsection{Instrumentation}
\label{sec:Instrumentation}
Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}. There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}. Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}. Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway. Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure. A single thermocouple was attached to each bi-directional probe. The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter. Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/BDPs}
\caption[Two sets of BDPs in Doorway of West Structure]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
\label{fig:BDPs}
\end{figure}

@@

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a monitor equipped with a combination nozzle. A schematic of the structure's layout during the two tests is presented in Fig.~\ref{fig:test_29-32_setup}. Each test began by flowing water with the nozzle aimed at the ceiling of Room C, as pictured in Fig.~\ref{fig:test_29_30_pic}. After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This entire procedure was repeated an additional time. A straight stream pattern was used during Test 29 and a narrow fog stream pattern was used during Test 30.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
\label{fig:test_29-32_setup}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and at Door BC (bottom row) during Tests 29 and 30}
\label{fig:test_29_30_pic}
\end{figure}
\FloatBarrier

Test 33 varied from Tests 29 and 30 in multiple ways. During Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as shown in Fig.~\ref{fig:test_33_pic}. A schematic of the structure's layout during Test 33 is presented in Fig.~\ref{fig:test_33_34_setup}. The test began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds. Then, the south side door was opened and each stream was applied for 30 seconds again.

\begin{figure}[!ht]
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/SS_Room_B_Test_33}
\\~\\
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/NF_Room_B_Test_33}
\\~\\
\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/WF_Room_B_Test_33}
\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 33]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 33}
\label{fig:test_33_pic}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
\label{fig:test_33_34_setup}
\end{figure}
\FloatBarrier

%ADD TARGET DIMENSION%
Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle. The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately X m (X ft) from the interior side of the north wall, and a "far" target, located approximately X m (X ft) from the interior side of the north wall. The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each test began by flowing water in a straight stream pattern at the far target for 60 seconds. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target. The entire process was repeated for the narrow fog and wide fog streams. Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure Layout for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure Layout for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/SS_near}
\end{center} 
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/NF_near}
\end{center}
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/WF_near}
\end{center}
\endminipage \hfill
\vspace{0.15in}
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/SS_far}
\end{center} 
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/NF_far}
\end{center}
\endminipage \hfill
\minipage{2.15in}
\begin{center}
	\includegraphics[width=2in]{../Pictures/WF_far}
\end{center}
\endminipage \hfill
\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Tests 16 and 17]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during Tests 16 and 17}
\label{fig:test_16_17_pic}
\end{figure}

@@

Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a combination nozzle attached to a 1.75" handline. The structure's layout during both tests was identical to the layout used in Tests 29 and 30 (Fig.~\ref{fig:test_29-32_setup}). Each test began by flowing water with the nozzle aimed at the ceiling of Room C in a fixed position, as pictured in Fig.~\ref{fig:test_31_32_pic}. After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction for 30 seconds and then returned to the fixed position for 30 seconds. Next, the nozzle was rotated in the counterclockwise direction for 30 seconds and then returned to the fixed position for 30 seconds. While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated. After the patterns were applied with the south side door opened, the door was closed, and the process was repeated with the handline aimed at Door BC. The entire procedure was then repeated an additional time. A straight stream pattern was used during Test 31 and a narrow fog stream pattern was used during Test 32.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
\label{fig:test_31_32_pic}
\end{figure}
\FloatBarrier

Test 34 varied from Tests 31 and 32 in multiple ways. During Test 34, the handline was located inside Room C. The structure's layout during Test 34 was identical to the layout used in Test 33 (Fig.~\ref{fig:test_33_34_setup}). The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}. Next, the nozzle was rotated in the clockwise direction for 30 seconds. Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern. This process were repeated for narrow fog and wide fog streams. Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.

%Where was the handline aimed?%
Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline. The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}). Each test began by flowing water in a straight stream pattern and fixed position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds. Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns. This entire procedure was repeated for narrow fog and wide fog streams.
